Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-16 paper/manuscript.tex
A bit of progress on results section 4

\subsection*{The selected mutations are in the binding footprints for all antibodies}
We visualized for each mutation the fraction surviving selection as a logoplot, and for each site mapped the mutation with the maximum fraction surviving selection onto the HA structure, shown in Figure~\ref{fig:structures}A. 
For all of the antibodies, the sites with mutations exhibiting the greatest fraction escape localize in the antibody epitope.

>>>>

\subsection*{The selected mutations are in the binding footprints for all antibodies}
We visualized for each mutation the fraction surviving selection as a logoplot, and for each site mapped the mutation with the maximum fraction surviving selection onto the HA structure, shown in Figure~\ref{fig:structures}A. 
For all of the antibodies, the sites with mutations exhibiting the greatest fraction escape localize in or near the antibody epitope.
Many amino-acid mutations at most sites can confer escape from the strain-specific antibodies and from S139/1. 
On the other hand, we see selection for only a handful of amino acids at sites of escape from the broad stalk-targeting antibodies.
